\section{Context}

\subsection{Curiosity Origin}
As frequent travelers, we are curious about urban mobility and how people navigate large cities.
We became particularly interested in understanding mobility patterns in the context of sustainable transportation and green alternatives—recognizing their growing importance in urban planning and environmental goals.
Specifically, we wanted to explore the underlying choices people make when selecting transportation modes and the factors that shape those decisions.

This curiosity led us to explore data sources that could provide meaningful insights into urban movement.
Among them, New York City's bike rental data stood out as a rich source of information on how people travel across the city using a sustainable mode of transportation.
When combined with other datasets, it can offer a clearer picture of the city's daily dynamics.

We also learned that this bike rental data is provided by a private company (\texttt{Citi Bike}) that operates the bike-sharing service in New York City.
For this reason, making our analysis useful and relevant to the company is an effective way to increase its practical impact.

\subsection{Project Circumstance and Purpose}
\texttt{Citi Bike} currently collects vast amounts of operational data. 
If effectively analyzed and visualized, this data could provide valuable insights to optimize their services and enhance user experience.

Our visualization tool directly addresses these gaps by making complex mobility data accessible and actionable.

The primary objective is to transform raw \texttt{Citi Bike} operational data into clear, actionable insights for stakeholders.

\subsubsection{Citi Bike Operations Team}
Specifically, we aim to reveal:
\begin{enumerate}
  \item \textbf{Temporal patterns}---peak usage hours, seasonal trends, and demand cyclicity.
  \item \textbf{Spatial hotspots}---high-demand stations, commute corridors, and underutilized infrastructure
  \item \textbf{User segmentation}---behavioral differences between members and casual riders
\end{enumerate}
The first two insights can help the operations team optimize station placement and bike rebalancing.
Meanwhile, the third can inform targeted marketing strategies and service improvements to better meet user needs.

\subsubsection{City Planners and General Public}
Beyond the operations team, our visualization can also benefit city planners by providing insights into commute flows and modal patterns, which can inform infrastructure investment and urban planning decisions.
For the general public, it can raise awareness of urban mobility and sustainable transportation alternatives, fostering a more informed and engaged community.

\subsection{Deliverables}

\subsubsection{Vision}
We deliver an interactive web-based dashboard as the primary output.
This allows all users to explore mobility patterns through a unified, user-friendly interface.
Our design approach is to present clear, immediate insights at first impactful while also allowing deeper exploration for users who want to examine the details.

Regarding update frequency, we expect the dashboard to be refreshed automatically on a regular basis, since the data are continuously collected.
This ensures that the insights remain useful and relevant over time, while also enabling historical analysis and comparisons across different periods.

\subsubsection{Design Philosophy}
Our visualization prioritizes clarity and analytical depth over visual polish.
We employ a dual-level approach: high-level dashboards present immediate summary insights (e.g., daily ridership totals, top stations), while detailed views enable granular exploration (e.g., hourly breakdowns, user type comparisons).
All design choices remain data-centric, avoiding decorative elements or misleading visual encodings that could obscure underlying patterns.

\subsubsection{Resources}
Since we are working with a large dataset and aim to create an interactive dashboard, we need programming skills and experience with data and visualization tools.

Our tech stack combines:
\begin{itemize}[beginpenalty=10000]
  \item \textbf{Backend (Python)} -- efficient data processing, cleaning, and REST API development via FastAPI;
  \item \textbf{Frontend (React/D3.js)} -- custom, interactive visualizations tailored to mobility pattern analysis.
\end{itemize}
This modular architecture enables rapid iteration during development while remaining scalable as data volumes grow.

\subsubsection{Constraints}
In general, trying to obtain the most value from the data while respecting project constraints is a key challenge. 
The project must balance the ambition of performing meaningful analyses with practical limitations such as time availability, data quality, and implementation complexity. 
Since the final deliverable is scheduled for June, it is necessary to keep the feature scope focused and prioritize analyses that can provide the most relevant and actionable insights.

Another important aspect concerns the quality and consistency of the available data. Historical \texttt{Citi Bike} records were collected over multiple years, 
and they may contain missing values, inconsistencies, or differences in formatting and schema across datasets. For this reason, a careful preprocessing phase is required to clean, 
standardize, and integrate the data before any reliable analysis can be performed.

Finally, the large size of the dataset introduces additional technical challenges. Efficient aggregation, filtering, 
and data handling strategies must be implemented to manage the volume of information effectively. 
These optimizations are particularly important to ensure that the dashboard remains responsive and interactive, allowing users to explore the data smoothly without performance issues.